---
title: "Trailer recommendations exploration"
output: html_notebook
---

```{r setup, echo=FALSE}
library(tidyverse)
```

This dataset was created by Eva Zhong, based on a movielens experiment 
led by Tahir Sousa.

The dataset contains one observation per user-login. A row appears for any user who viewed one or more movie trailers during their session.  The Algorithm represents a recommendation algorithm they were given, which was randomly assigned on each login.

* `count_total_played` -- total number of movie trailers started during the login session
* `count_rec_played` -- total number of movie trailers played *from a list of recommendations* started during the login session

```{r read-dataset, echo=FALSE}
trailer_activities <- readRDS("./trailer_activies.rds")
trailer_activities
```

## task: make a histogram

* plot a histogram of `count_total_played` using `geom_histogram`
* try setting `binwidth` in geom_histogram
* try adding `coord_cartesian(xlim = c(0, 20))` (or, try using a ylim)


## task: make scatter plots

Plot the relationship between `count_total_played` and `count_rec_played` using:

* geom_point (try setting `alpha=0.1`)
* geom_jitter
* geom_count

Also:

* use a `facet_wrap` to split the chart by algorithm


## summary stats

Here are aggregate stats of recommended play actions, grouped by algorithm:

```{r summary-stats}
trailer_activities_summary <- trailer_activities %>% 
  group_by(Algorithm) %>% 
  summarise(
    total_played = n(),
    mean_rec_played = mean(count_rec_played),
    max_rec_played = max(count_rec_played),
    min_rec_played = min(count_rec_played),
    std_err_rec_played = sd(count_rec_played)/sqrt(n())
  )
trailer_activities_summary
```


## task: make a bar chart!

Are the number of observations balanced between the four experimental algorithms?
Build a bar chart of this tibble by Algorithm.

* use `geom_col`, charting Algorithm by mean_rec_played
* try adding another geom: `geom_errorbar(aes(ymin = mean_rec_played - std_err_rec_played, ymax = mean_rec_played + std_err_rec_played))`
    
