---
title: "Trailer recommendations exploration"
output: html_notebook
---

```{r setup, echo=FALSE}
library(tidyverse)
```


This dataset was created by Eva Zhong, based on a movielens experiment 
led by Tahir Sousa.

The dataset contains one observation per user-login. A row appears for any user who viewed one or more movie trailers during their session.  The Algorithm represents a recommendation algorithm they were given, which was randomly assigned on each login.

```{r read-dataset, echo=FALSE}
conditions <- c("ShuffledTopPicks", "TagSimilarity", "PredictedRating", "FilmReleaseDate")
trailer_activities <- readr::read_csv("trailer_activities.csv",
                                          col_types = cols_only(
                                            userId = col_character(),
                                            loginId = col_character(),
                                            Algorithm = col_factor(conditions, ordered = TRUE),
                                            count_total_played = col_integer(),
                                            count_rec_played = col_double(),
                                            count_refresh = col_double()
                                          ))
trailer_activities
```

Some users viewed lots of trailers! Here are some summary stats:

```{r summary-stats, echo=FALSE}
trailer_activities %>% 
  group_by(Algorithm) %>% 
  summarise(
    total_played = n(),
    mean_played = mean(count_total_played),
    max_played = max(count_total_played),
    min_played = min(count_total_played),
    sd_PL = sd(count_total_played),
    SE_PL = sd(count_total_played)/sqrt(n())
  )
```


## histograms!

Plot a histogram of `count_total_played` using `geom_histogram`.

* try `binwidth` in geom_histogram
* try adding `coord_cartesian(xlim = c(0, 20))` (or with ylim)


```{r}
1 + 1
```



```{r}
ggplot(trailer_activities, mapping=aes(x=count_refresh)) +
  geom_histogram(binwidth=1) +
  coord_cartesian(ylim = c(0, 1000))
```


hello, world!




## scatter plots!

Plot the relationship between `count_total_played` and `count_rec_played` using:

* geom_point (try setting `alpha=0.1`)
* geom_jitter
* geom_count


```{r foo}
ggplot(trailer_activities, mapping=aes(x=count_total_played, y=count_rec_played)) +
  geom_point(alpha=0.1)
```



## bar charts!

Visualize `count_rec_played` across the four algorithms using a bar chart 


```{r}
ggplot(trailer_activities, mapping=aes(x=count_total_played, y=count_rec_played)) +
  geom_jitter()
```

```{r}
ggplot(trailer_activities, mapping=aes(x=count_total_played, y=count_rec_played)) +
  geom_jitter() +
  facet_wrap(~ Algorithm)
```

